%Read the slack post (link below) regarding syntax and formatting before you start writing lecture notes.
% Post: https://musa-2021.slack.com/archives/C01DGR645SL/p1609187728029500



\documentclass[../notes.tex]{subfiles}
\begin{document}

\stepcounter{week}
\section{Week \theweek: Introduction to Proofs}
In this section, we discuss proofs. Of course, we have already seen a few proofs previously in \cref{ch:set}, but we will now introduce proofs more formally on their own terms.

\subsection{Proof Basics}
The best way to learn what a proof is to see some examples. Here's an example from high-school algebra.
\begin{example}
    Set $p(x) \coloneqq x^2 + bx + c$ for some real numbers $b$ and $c$. If $r_1,r_2$ are the zeroes of $p$, then $r_1 + r_2 = -b$, and $r_1r_2 = c$.
\end{example}
\begin{proof}
    We want to start any proof by writing down the basic definitions and properties. We know that $r_1$ and $r_2$ are zeroes, so $p(r_1) = p(r_2) = 0$. It follows that we can factor
    \[p(x)=(x-r_1)(x-r_2)\]
    because the leading coefficient on the $x^2$ term of $p(x)$ is $1$. Expanding both sides,
    \[x^2 + bx + c = x^2 - (r_1 + r_2)x + r_1r_2,\]
    so $r_1 + r_2 = -b$ and $r_1r_2 = c$.
\end{proof}
That proof should convince you beyond a shadow of a doubt that the claim is true, assuming that you know basic facts about quadratics: above all, a proof is an argument, meant to persuade the reader. If it didn't, think about it and figure out where you lost the line of reasoning, and ask around. Often a proof might not make sense when we read it ourselves, but it becomes clearer when someone else explains it. Here are a few more examples.
\begin{example} \label{exe:squares-even}
    Let $n$ be an integer. If $n$ is even, then $n^2$ is even.
\end{example}
\begin{proof}
    Again, we start by writing down the definition. If $n$ is even, then there exists another natural number $k$ such that $n = 2k$. Then
    \begin{align*}
        n^2 &= (2k)^2\\
        &= 4k^2\\
        &= 2 \cdot 2k^2.
    \end{align*}
    We have shown that $n^2$ is $2$ times the natural number $2k^2$, so $n^2$ is an even number by definition.
\end{proof}
The following are examples using the language of set theory, which we introduced in \cref{ch:set}. In the interest of using knowledge we have definitely built, many of the problems at the end of this section will also use the language of set theory.
\begin{example}
    Let $A$ and $B$ and $C$ be sets. If $A\subseteq B$ and $B\subseteq C$, then $A\subseteq C$.
\end{example}
\begin{proof}
    We want to show that $A\subseteq C$. In other words, for any $a\in A$, we want to show that $a\in C$. Well, we know that $A\subseteq B$, so $a\in A$ implies $a\in B$. Continuing, we know that $B\subseteq C$, so $a\in B$ implies $a\in C$, which is what we wanted.
\end{proof}
\begin{example}
    Let $\preceq$ be a partial order on the set $X$. If $a\preceq b$ and $b\preceq c$ and $c\preceq a$, then $a=b$ and $b=c$.
\end{example}
\begin{proof}
    We have two claims to show: we want to show that $a=b$ and $b=c$. We will show these separately.
    \begin{itemize}
        \item We show that $a=b$. We know that $b\preceq c$ and $c\preceq a$, so $b\preceq a$ follows because $\preceq$ is a partial order and hence transitive. But we already know that $a\preceq b$, so because $\preceq$ is antisymmetric, we see that $a=b$.
        \item We show that $b=c$. We know that $c\preceq a$ and $a\preceq b$, so because $\preceq$ is transitive, $c\preceq b$. However, $b\preceq c$ already, so because $\preceq$ is antisymmetric, it follows $b=c$.
        \qedhere
    \end{itemize}
\end{proof}
\begin{example}
    Let $X$ be a set, and let $\sim$ be an equivalence relation which is also a partial order. Then for any $x_1,x_2\in X$, we have $x_1\sim x_2$ if and only if $x_1=x_2$.
\end{example}
\begin{proof}
    Here is an important piece of language: ``if and only if'' means that we will want to show both that $x_1\sim x_2$ implies that $x_1=x_2$ and that $x_1=x_2$ implies $x_1\sim x_2$. We show these implications separately.
    \begin{itemize}
        \item Suppose $x_1\sim x_2$. Because $\sim$ is an equivalence relation, it is symmetric, so $x_2\sim x_1$. However, $\sim$ is a partial order, so $x_1\sim x_2$ and $x_2\sim x_1$ implies that $x_1=x_2$.
        \item Suppose $x_1=x_2$. Because $\sim$ is an equivalence relation, it is reflexive, so $x_1\sim x_2$.
    \end{itemize}
    The above implications complete the proof!
\end{proof}
Let's try a harder example. See if you can follow the logic! How might you have come up with the argument on your own?
\begin{example} \label{ex:equiv-partition}
    Let $\sim$ be an equivalence relation on $X$. For $x\in X$ recall that the equivalence class of $x$ is the subset
    \[[x]\coloneqq\{x'\in X:x\sim x'\}.\]
    For $x_1,x_2\in X$, we have $x_1\sim x_2$ if and only if $[x_1]=[x_2]$.
\end{example}
\begin{proof}
    Recall from the previous example that ``if and only if'' means that we will want to show both that $x_1\sim x_2$ implies $[x_1]=[x_2]$ and that $[x_1]=[x_2]$ implies $x_1\sim x_2$. We show these implications separately.
    \begin{itemize}
        \item Suppose $x_1\sim x_2$. Then we want to show $[x_1]=[x_2]$. To show that $[x_1]=[x_2]$, we use \Cref{prop:subset-reflexive}: we show that $[x_1]\subseteq[x_2]$ and that $[x_2]\subseteq[x_1]$.

        To see that $[x_1]\subseteq[x_2]$, choose any $y\in[x_1]$, and we want to show $y\in[x_2]$. Well, $y\in[x_1]$ means that $x_1\sim y$. However, $x_1\sim x_2$ already, so $x_2\sim x_1$ and $x_1\sim y$ implies that $x_2\sim y$. It follows $y\in[x_2]$.

        Showing that $[x_2]\subseteq[x_1]$ is identical: for any $y\in[x_2]$, we know $x_2\sim y$, but $x_1\sim x_2$, so we see $x_1\sim y$, meaning $y\in[x_1]$. This completes the proof.

        \item Suppose $[x_1]=[x_2]$. Then we note that $x_1\sim x_1$, so $x_1\in[x_1]$, from which it follows $x_1\in[x_2]$ by the equality of our sets. This then means that $x_1\sim x_2$.
    \end{itemize}
    The above implications completes the proof.
\end{proof}
% Let's try a harder example. It is the converse for \Cref{prop:function-to-equiv}. See if you can follow the logic! How might you have come up with the argument on your own?
% \begin{example}
%     Let $\sim$ be an equivalence relation on $X$. Then there is a set $Y$ and a function $f\colon X\to Y$ such that $x_1\sim x_2$ if and only if $f(x_1)=f(x_2)$.
% \end{example}
% \begin{proof}
%     The difficulty in this argument lies in constructing the set $Y$. For a given $x\in X$, recall that $[x]$ denotes the equivalence class of $x$, which is
%     \[[x]=\{x'\in X:x'\sim x\}.\]
%     Note $[x]$ is a subset of $X$. The key point is the definition $Y\coloneqq\{[x]:x\in X\}$ and then the function $f\colon X\to Y$ by $f(x)\coloneqq[x]$. This function $f$ is in fact well-defined, though the concerned reader should check it.

%     We now show that the function $f$ has $x_1\sim x_2$ if and only if $f(x_1)=f(x_2)$. However, this is simply \Cref{ex:equiv-partition}, so we are done.
% \end{proof}
% \begin{example}[Euler's formula]
%     For all real numbers $x$,
%     \[e^{ix} = \cos x + i \sin x.\]
% \end{example}
% \begin{proof}
%     At first this might seem a bit hopeless, because it's not clear that $\exp$ and the trigonometric functions have anything to do with each other. The first clue to consider is that the derivative $\frac ddx\exp(x) = \exp(x)$, while $\frac d{dx}\sin(x) = \cos(x)$, and $\frac d{dx}\cos(x) = -\sin(x)$. So it's very easy to compute the higher derivatives of these functions, which means we can reason using Taylor series. This is as good a place to start as any, so we'll try this and see what happens.

%     Recall the Taylor series
%     \[e^x = \sum_{n=0}^\infty \frac{\exp^{(n)}(0)}{n!} x^n = \sum_{n=0}^\infty \frac{e^0}{n!} x^n = \sum_{n=0}^\infty \frac{x^n}{n!}.\]
%     Similarly,
%     \begin{align*}
%         \cos x &= 1 - \frac{x^2}{2!} + \frac{x^4}{4!} - \frac{x^6}{6!} + \cdots \\
%         \sin x &= x - \frac{x^3}{3!} + \frac{x^5}{5!} - \frac{x^7}{7!} - \cdots.
%     \end{align*}
%     Plugging in $ix$ to $e^x$ and using that $i^2 = -1$, we have
%     \begin{align*}
%         e^{ix} &= 1 + ix + \frac{(ix)^2}{2!} + \frac{(ix)^3}{3!} + \frac{(ix)^4}{4!} + \dots \\
%         &= 1 + ix + \frac{-x^2}{2!} - i\frac{x^3}{3!} + \frac{x^4}{4!} + \dots\\
%         &= \left(1 - \frac{x^2}{2!} + \frac{x^4}{4!} - \dots\right) + i\left(x - \frac{x^3}{3!} + \frac{x^5}{5!} - \dots\right)\\
%         &= \cos x + i\sin x,
%     \end{align*}
%     so $e^{ix} = \cos x + i\sin x$.
% \end{proof}
% It can be helpful to break up a big proof into lots of smaller parts, called ``lemmas,'' and work on each one separately.
Notice that in all of the above proofs, we needed to use every assumption we made. This will be the case on the homework. In other words, if you finished a proof and didn't use some assumption that the theorem made, then something went wrong. Explicitly, one of the following happened.
\begin{itemize}
    \item You assumed too much. In this case, the statement of the theorem you were trying to prove should be rephrased without the unnecessary assumptions.
    \item You used the assumption tacitly in part of the proof, without realizing it. In this case, realize where you used the assumption, and note it explicitly.
    \item You made an error elsewhere in the proof. In this case, fix your proof!
\end{itemize}
In general, if you prove a theorem but didn't use one of your assumptions, then you have proven a stronger theorem!

Let's see another example. Keep track of where we use the fact that $\triangle ABC$ is a right triangle in the following proof!
\begin{example}[Pythagorean theorem] \nirindex{Pythagorean theorem} \label{exe:pythag-thm}
    Let $\triangle ABC$ be a right triangle with right angle $C$. Setting $a\coloneqq BC$ and $b\coloneqq CA$ and $c\coloneqq AB$, then
    \[a^2 + b^2 = c^2.\]
\end{example}
\begin{proof}
    We must show $BC^2 + CA^2 = AB^2$. Let $H$ be the point on the hypotenuse such that $\angle CHA$ is a right angle, which gives the following diagram.
    \begin{center}
        \begin{asy}
            unitsize(0.7cm);
            pair B=(0,3), C=(0,0), A=(4,0), H=(13/9,23/12);
            draw(A -- B -- C -- cycle);
            draw(C -- H);
            dot("$A$", A, ESE);
            dot("$B$", B, NNW);
            dot("$C$", C, SW);
            dot("$H$", H, NE);
        \end{asy}
    \end{center}
    We claim that $\triangle ACH$ is similar to $\triangle ABC$. Indeed, $\angle AHC=\angle ACB$ because both are right angles, and $\angle BAC=\angle CAH$ because those are literally the same angle. Lastly, because the angles in both triangles must add up to $180^\circ$ degrees, we must have
    \[\angle ABC + \angle BCA + \angle CAB = 180^\circ = \angle ACH + \angle CHA + \angle HAC,\]
    so $\angle ACH = \angle ABC = 90^\circ - \angle BAC$. Thus, the triangles are similar. A similar proof shows $\triangle CBH$ is similar to $\triangle ABC$. (Show this yourself, if you'd like.)

    Using our similar triangles, we see
    \[\frac{CA}{AB} = \frac{HA}{AC}\qquad\text{and}\qquad\frac{BC}{AB} = \frac{BH}{CB}.\]
    Thus, $BC^2 = AB\cdot BH$ and $AC^2 = AB\cdot AH$, so
    \[BC^2 + AC^2 = AB\cdot BH + AB\cdot AH = AB(AH + BH) = AB^2.\]
    This proves the claim.
\end{proof}
\begin{remark}
    If the proof of \Cref{exe:pythag-thm} did not use the condition that $\triangle ABC$ was a right triangle, then we would have proven the stronger claim that any triangle $\triangle ABC$ has
    \[BC^2+CA^2=AB^2.\]
    However, this claim is false! For example, there is an equilateral triangle with $AB=BC=CA=1$, and $1^2+1^2\ne1^2$. This equilateral triangle is called a ``counterexample'' to our statement.
\end{remark}
We close this subsection with an example from linear algebra.
\begin{example} % \label{kernel is subspace}
    Let $T\colon V \to W$ be a linear transformation between vector spaces over the scalar field $F$. Then the kernel $\ker(T)$ of $T$ is a vector subspace of $V$.
\end{example}
\begin{proof}
    By definition, the kernel is
    \[\ker(T) \coloneqq \{v \in V: T(v) = 0\},\]
    where $0$ is the zero vector of $W$.
    
    Now, recall the definition of subspace of a vector space: a set $S$ is a subspace of $V$ if $S$ is a subset of $V$ that contains the zero vector $0_V$ and is closed under vector addition and scalar multiplication. Therefore, we must check that $\ker(T)$ fulfills all three of the necessary conditions to be a subspace of $V$.
    \begin{itemize}
        \item By definition, we see $\ker(T)$ is a subset of $V$.
        \item It is a property of linear transformations that $T(0_V)=0_W$. To see this, note $0_V+0_V=0_V$, so because $T$ is a linear transformation,
        \[T(0_V)+T(0_V)=T(0_V+0_V)=T(0_V).\]
        Rearranging gives $T(0_V)=0_W$, so $0_V$ is in $\ker(T)$.
        \item We check that $\ker(T)$ is closed under addition. Well, given two arbitrary vectors $v$ and $w$ in $\ker(T)$, we must show their sum $v+w$ is also in $\ker(T)$. Because $T$ is a linear transformation,
        \[T(v+w)=T(v)+T(w).\]
        Now, we use our assumption that $v$ and $w$ were in $\ker(T)$. This means we know $T(v) = 0_W$ and $T(w) = 0_W$, so
        \[T(v+w)=0_W+0_W=0_W.\]
        It follows $v+w$ is in $\ker(T)$.
        \item We check that $\ker(T)$ is closed under scalar multiplication. Well, given a vector $v$ in $\ker(T)$ and a scalar $k$ in $F$, we must show $k\cdot v$ is also in $\ker(T)$. Because $T$ is a linear transformation, we compute
        \[T(k\cdot v)=k\cdot T(v).\]
        However, because $v$ is in $\ker(T)$, we see $T(v)=0_V$. To finish, we use properties of the zero vector to give
        \[T(k\cdot v)=k\cdot 0_V=0_V.\]
        It follows $k\cdot v$ is in $\ker(T)$.
        \qedhere
    \end{itemize}
\end{proof}

\subsection{Contradiction and Contraposition}
In order to prove that a statement is true, it is sometimes easier to do so when an extra assumption, let's say $P$, is true. If another proof proves the statement when $P$ is false, then together the two proofs imply that the statement is true. This is called ``proof by cases.''
\begin{example}
    There exist irrational real numbers $x$ and $y$ such that $x^y$ is rational.
\end{example}
\begin{proof}
    You will prove in the homework that $\sqrt{2}$ is irrational. For now, assume that $\sqrt{2}$ is irrational. We know $\sqrt{2}^{\sqrt{2}}$ must be either rational or irrational. So, we divide our proof into two cases.
    \begin{itemize}
        \item Suppose $\sqrt{2}^{\sqrt{2}}$ is rational. Then we have found irrational numbers $x$ and $y$, with $x = y = \sqrt{2}$, such that $x^y$ is rational.
        \item Suppose $\sqrt{2}^{\sqrt{2}}$ is irrational. Let $x = \sqrt{2}^{\sqrt{2}}$ and $y = \sqrt{2}$. Then
        \[x^y = \left(\sqrt{2}^{\sqrt{2}}\right)^{\sqrt{2}} = \sqrt{2}^{\sqrt{2} \cdot \sqrt{2}} = \sqrt{2}^2 = 2.\]
        Because $x^y=2$ is rational, we have found irrational numbers $x$ and $y$, with $x = \sqrt{2}^{\sqrt{2}}$ and $y = \sqrt{2}$, such that $x^y$ is rational. 
    \end{itemize}
    Because one of the above cases must hold, and in both cases such $x$ and $y$ exist, the statement must be true.
\end{proof}
This proof is ``non-constructive.'' Namely, the proof does not tell us the explicit $x$ and $y$ such that the statement holds; rather, the proof only verifies that such $x$ and $y$ exist. You will encounter plenty of non-constructive proofs in your upper division math classes.
\begin{remark}
    It turns out that $\sqrt{2}^{\sqrt{2}}$ is irrational, as in the second case above, but proving this is non-trivial. For the interested, it is a consequence of the Gelfond--Schneider theorem.
\end{remark}
Now let's see an example that we'll come back to later: Russell's paradox. It's a silly, but very important, example of a ``proof by contradiction.''
\begin{example} \label{exe:barber-diagonalization} %\index{Russell's paradox}
    It is impossible for a barber to say that he will shave people if and only if they do not shave themselves.
\end{example}
\begin{proof}
    For a proof by contradiction, we are going to suppose that such a barber exists, and then show that the existence of the barber implies a contradiction. It will then follow that the barber could not exist!
    
    Indeed, suppose that such a barber exists. Either the barber shaves himself or he does not shave himself, which gives the following cases.
    \begin{itemize}
        \item Suppose that the barber shaves himself. If so, then he does not shave himself, so he both shaves himself and does not shave himself. This is impossible.
        \item Suppose the barber does not shave himself. But then he shaves himself, which is still impossible.
    \end{itemize}
    All cases have led to impossibility, so the barber does not exist.
\end{proof}
Here are some more proofs by contradiction.
\begin{example}
    Let $X$ be a nonempty set. There is no function $f\colon X\to\emp$.
\end{example}
\begin{proof}
    Suppose for the sake of contradiction we have a function $f\colon X\to\emp$. We know that $X$ is nonempty, so we may find some $x\in X$. Because $f$ is a function, it follows $f(x)\in\emp$. However, this is a contradiction because $\emp$ has no elements!
\end{proof}
\begin{example}
    Let $A$ and $B$ be sets. Then $(A\setminus B)\cap(A\cap B)=\emp$.
\end{example}
\begin{proof}
    Suppose for the sake of contradiction that we have an element $a\in(A\setminus B)\cap(A\cap B)$. Then $a\in A\setminus B$, so it follows that $a\notin B$. On the other hand, $a\in A\cap B$, so it follows that $a\in B$. However, this is a contradiction! As such, $(A\setminus B)\cap(A\cap B)$ must have no elements.
\end{proof}
\begin{example} \label{exe:odd-square-to-odd}
    Let $n$ be an integer. If $n^2$ is odd, then $n$ is odd.
\end{example}
\begin{proof}
    Suppose for the sake of contradiction that $n$ is not odd, so $n$ is even. But then $n^2$ is even by \Cref{exe:squares-even}! This is a contradiction because we know $n^2$ is supposed to be odd. Thus, we must instead have $n$ being odd.
\end{proof}
A proof technique similar to contradiction is contraposition. To understand contraposition, recall that
\[(p\to q)\equiv(\lnot q\to\lnot p)\]
by \Cref{ex:contraposition}. As such, sometimes when we want to show a statement of the form $p\to q$, we can try to prove the contraposition $\lnot q\to\lnot p$ instead. Our first example is revamping the proof of \Cref{exe:odd-square-to-odd}.
\begin{proof}[Another proof]
    The contraposition of ``if $n^2$ is odd, then $n$ is odd'' is the statement ``if $n$ is not odd, then $n^2$ is not odd.'' However, a positive integer is ``not odd'' if and only if it is even, so we're actually proving ``if $n$ is even, then $n^2$ is even,'' which is exactly \Cref{exe:squares-even}.
\end{proof}
Here's a similar example for you to try.
\begin{exe}
    Let $n$ be an integer. If $n^2$ is even, then $n$ is even.
\end{exe}

\subsection{Uniqueness Proofs}
Sometimes we will want to prove that some object is unique. The usual way to do this is to suppose that any two such objects are equal. Let's see some examples.
\begin{example} \label{exe:increasing-is-injective}
    Let $f$ be a strictly increasing function from the real numbers to the real numbers. Then for each real number $y$, there is at most real number $x$ such that $f(x)=y$.
\end{example}
\begin{proof}
    Suppose that we have real numbers $x$ and $x'$ such that $f(x)=y$ and $f(x')=y$. We show $x=x'$. There are three cases.
    \begin{itemize}
        \item If $x<x'$, then $f(x)<f(x')$, so $y<y$, which is impossible.
        \item If $x=x'$, then we are done.
        \item If $x>x'$, then $f(x)>f(x')$, so $y>y$, which is impossible.
    \end{itemize}
    All cases give impossibility or $x=x'$, so we conclude $x=x'$.
\end{proof}
Note that third case of the previous proof was identical to the first case with some letters changed. In the future, we might say ``without loss of generality, we have $x>x'$ or $x=x'$ because the case of $x'<x$ is similar.''

Continuing with our examples, here are a few from our language of set theory.
\begin{example}
    Let $A$ and $B$ be sets with one element. Then there is a unique function $f\colon A\to B$.
\end{example}
\begin{proof}
    Because $A$ and $B$ have one element, we may write $A=\{a\}$ and $B=\{b\}$ for some $a\in A$ and $b\in B$.

    Now, before proving the uniqueness of the function $f$, we note that there certainly is a function $f\colon A\to B$. Indeed, simply define $f$ by $f(a)\coloneqq b$. It remains to show that this $f$ is unique.

    Well, suppose that $g\colon A\to B$ is another function. Then we know that $g(a)\in B$, but $B$ has only element, so $g(a)=b$ follows. Thus, we see that $f(a)=g(a)$, and because $a$ is the only element of $A$, it follows that $f$ and $g$ are equal as functions. This completes the proof of uniqueness.
\end{proof}
\begin{example} \label{ex:unique-minimum-poset}
    Let $\preceq$ be a partial order on the set $X$. There is at most one element $x_0\in X$ with the property that $x_0\preceq x$ for all $x\in X$.
\end{example}
\begin{proof}
    Suppose we have two such elements $x_0$ and $x_0'$. By definition of $x_0$, we know that $x_0\preceq x_0'$. On the other hand, by definition of $x_0'$, we know that $x_0'\preceq x_0$. So because $\preceq$ is antisymmetric, the previous two sentences imply $x_0=x_0'$.
\end{proof}
\begin{remark}
    An element of a partial order satisfying the conclusion of \Cref{ex:unique-minimum-poset} is called a ``minimum'' of the partially ordered set $X$. Do you see why?
\end{remark}
% \begin{example}
%     Say that a function $f$ from the real numbers to the real numbers is ``strictly convex'' if $f$ is twice-differentiable and $f''(t) > 0$ for all real numbers $t$. If $f$ is strictly convex, then there exists at most one real number $x$ such that $f(x)$ is the (global) minimum value of $f$.
% \end{example}
% \begin{proof}
%     Assume that $f$ achieves its minimum at $x$ and $x'$.
%     % Without loss of generality, we can assume that $x \leq x'$ because the case of $x'\ge x$ is similar.
%     % This means that we are making a harmless assumption: we do not know much about $x$ and $y$, but either $x \leq y$ or $x \leq y$. The proofs will be exactly the same in either case but with the variables swapped, so we might as well assume $x \leq y$.
%     By some calculus, we can compute the derivatives $f'(x) = 0$ and $f'(x') = 0$. On the other hand, since $f''(t) > 0$ for all $t$, we see $f'$ is strictly increasing, so $f'(x)=f'(x')$ implies $x=y$ by \Cref{exe:increasing-is-injective}.
% \end{proof}
Our last example of this subsection will be relevant to us when we study group theory in \Cref{ch:grp}.
\begin{example}
    There exists exactly one real number $z$ such that $z+a=a+z=a$ for all real numbers $a$. %The additive identity of a vector space is unique. %TODO Replace with not linear algebra
\end{example}
\begin{proof}
    Before jumping into the uniqueness part of this proof, we see that there are at least one real number $z$ because $z=0$ will work: $0+a=a+0=a$ for all real numbers $a$.

    We now show uniqueness. Suppose there are two such real numbers $z$ and $z'$. The trick, now, is to compute $z+z'$ in two ways: we see
    \[z+z'=z\qquad\text{and}\qquad z+z'=z'.\]
    Thus, $z=z'$.
    % Let $V$ be a vector space. To show that the additive identity of $V$ is unique, we will suppose there are two instances of the additive identity, $0$ and $0'$, in $V$, and show that they are in fact equal. Let $v \in V$. Then
    % \begin{align*}
    %     v + 0 &= v + 0'
    %     \intertext{Since $V$ is a vector space, $v$ has an additive inverse $-v$. Adding $-v$ to each side yields}
    %     v + 0 + (-v) &= v + 0' + (-v)\\
    %     0 + 0 &= 0 + 0'\\
    %     0 &= 0'
    % \end{align*}
    % Conclude that the additive identity of a vector space is unique.
\end{proof}
If you made it this far, then the discussion problems below should not be conceptually too difficult. Focus on writing neat, complete, and rigorous proofs.
\begin{exercise}
    We know that if a natural number $n$ is even, then there is another natural number $k$ such that $n = 2k$. Prove that this $k$ is unique.
\end{exercise}
\begin{exercise}
    Let $q$ be a non-zero rational number. Prove that $q$ has a unique multiplicative inverse; that is, there exists a unique rational number $r$ such that $qr = 1$.
\end{exercise}
\begin{exercise}
    Show that the set of rational numbers $\QQ$ is closed under addition and multiplication. Is the set $\RR \setminus \QQ$ of irrational numbers also closed under addition and multiplication? If so, prove it, and if not, find a counterexample.
\end{exercise}

\subsection{Problems}
\begin{homework}[triangle inequality]
    %\index{triangle inequality}
    %\label{triangle ineq}
    Prove the following.
    \begin{enumerate}[label=(\alph*)]
        \item For any real numbers $a$ and $b$,
        \[|a+b|\le|a|+|b|.\]
        \item For any real numbers $x$, $y$, and $z$,
        \[|x-z|\le|x-y|+|y-z|.\]
        \item For any vectors $u$, $v$, and $w$ in $\mathbb R^3$,
        \[\lVert u-w\rVert\le\lVert u-v\rVert+\lVert v-w\rVert,\]
        where $\lVert z\rVert$ denotes the length of a vector $z$ in $\mathbb R^3$.
    \end{enumerate}
\end{homework}

\begin{homework}
    Prove that if $n$ is an integer, then $3n^2 + n + 10$ is even.
\end{homework}

\begin{homework}
    Prove the following.
    \begin{enumerate}[label=(\alph*)]
        \item If $x$ is even and $y$ is odd then $x + y$ is odd.
        \item If $x$ and $y$ are both even then $x + y$ is even.
        \item If $x$ and $y$ are both odd then $x + y$ is even.
        \item If $x$ is even and $y$ is even then $xy$ is even.
        \item If $x$ is odd and $y$ is even then $xy$ is even.
        \item If $x$ and $y$ are both odd then $xy$ is odd.
    \end{enumerate}
\end{homework}

\begin{homework}
    Show that $\sqrt[3]{2}$ is irrational.
\end{homework}

\begin{homework}
    Suppose $A, B, C$ are subsets of $X$. Write $A \operatorname{\triangle} B$ for the \dfn{symmetric difference} of $A$ and $B$ in $X$, which is
    $$A \operatorname{\triangle} B = (A \setminus B) \cup (B \setminus A).$$
    In the Venn diagram of $A$ and $B$, $A \operatorname{\triangle} B$ consists of the parts of the diagram that are in exactly one of $A$ and $B$, but not both.
    
    Provide explanations for the following.
    \begin{enumerate}[label=(\alph*)]
        \item $x \in X$ has $x \in A \operatorname{\triangle} B$ if and only if $x \in A$ or $x \in B$ but not both.
        \item $(A \operatorname{\triangle} B) \operatorname{\triangle} {(B \operatorname{\triangle} C)} = A \operatorname{\triangle} C$. (Hint: break each step into cases and apply part 1)
        %Removed part 3 because this problem is already very long, and the last part is not very interesting
        %\item $A \cap (B \Delta C) = (A \cap B) \Delta (A \cap C)$.
        \item $(A \operatorname{\triangle} B)\operatorname{\triangle}C=A\operatorname{\triangle}{}(B\operatorname{\triangle}C)$.
        \item $A\cap(B\operatorname{\triangle}C)=(A\cap B)\operatorname{\triangle}{}(A\cap C)$.
    \end{enumerate}
\end{homework}

\begin{homework}
    Let $\sim$ be an equivelence relation on $X$, and let
    \[X/{\sim}\coloneqq\{[x]:x\in X\}\]
    denote the set of equivalence relations on $X$. Define the function $p\colon X\to(X/{\sim})$ by $p(x)\coloneqq[x]$. For any $x_1,x_2\in X$, prove that $x_1\sim x_2$ if and only if $p(x_1)=p(x_2)$.
\end{homework}

\begin{homework}
    Let $\sim$ be an equivalence relation on $X$. For any $x_1,x_2\in X$, show that $[x_1]\cap[x_2]$ is nonempty if and only if $[x_1]=[x_2]$.
\end{homework}

\begin{homework}
    Let $X$ be the set $\{1,2\}$.
    \begin{listalph}
        \item Write down four distinct functions $f_1,f_2,f_3,f_4\colon X\to X$.
        \item Let $f\colon X\to X$ be any function. Prove that $f=f_i$ for one of the functions $f_i$ found in (a).
    \end{listalph}
\end{homework}

\begin{homework}
    Let $A$, $B$, and $C$ be sets. Show that $(A\cap C)\cap((A\cup B)\setminus C)=\emp$.
\end{homework}

% \begin{homework}
%     Let $(V, \bigoplus _{V}, \bigotimes _{V})$ and $(W, \bigoplus _{W}, \bigotimes _{W})$ be vector spaces over the field $F$. Let $T: V \rightarrow W$ be a linear transformation. Verify that, in fact, $\ker(T)$ is closed under scalar multiplication. 
% \end{homework}

\end{document}